Tree regeneration in models of forest dynamics: a key priority for further research

### 2023-04-28 manuscript/manuscriptRW.Rmd
fix merge issues on the abstract

---
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
---

@@

Most of the models overestimate regeneration levels, which is only
compensated by some models with high simulated mortality rates in the
early stages of individual trees dynamics. Simulated species diversity
of regeneration matches the observed ranges. Models simulating higher
species diversity at the stand level do not feature higher regeneration
diversity. The effect of light availability on regeneration levels is
captured better than the effect of temperature and soil moisture, but
patterns are not consistent across models. Increasing complexity in the
tree regeneration modules of the models is not related to higher
accuracy of simulated tree regeneration. Furthermore, individual model
design is more important than scale (stand, landscape, global) and
approach (empirical, process-based) for accurately capturing tree
regeneration.

Despite considerable mismatches between simulation results and data in
some instances, it is remarkable that most of the models capture the
essential features of the highly complex process of tree regeneration,
while not having been parameterized with such data. We conclude that
much can be gained by evaluating and refining model regeneration
processes. This has the potential to render long-term projections of
forest dynamics under changing environmental conditions that are much
more robust.

>>>>

---
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
author:
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Mats Mahnken,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: template_paper.docx
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
---

@@

Most of the models overestimate regeneration levels, which is only
compensated in some models by high simulated mortality rates in the
early stages of individual trees dynamics. Simulated species diversity
of regeneration matches the observed ranges. Models simulating higher
species diversity at the stand level do not feature higher regeneration
diversity. The effect of light availability on regeneration levels is
captured better than the effect of temperature and soil moisture, but
patterns are not consistent across models. Increasing complexity in the
tree regeneration modules of the models is not related to higher
accuracy of simulated tree regeneration. Furthermore, individual model
design is more important than scale (stand, landscape, global) and
approach (empirical, process-based) for accurately capturing tree
regeneration.

Despite considerable mismatches between simulation results and data, it is remarkable that most models capture the
essential features of the highly complex process of tree regeneration,
while not having been parameterized with such data. We conclude that
much can be gained by evaluating and refining the modeling of regeneration
processes. This has the potential to render long-term projections of
forest dynamics under changing environmental conditions that are much
more robust.
